Orchestrating stencils with the Multi-Stencil Framework

### 2017-03-02 ARTICLES/IJPP/articleR1/evaluation.tex
new results + new structure evaluation

\begin{figure}[ht]
\begin{center}
\subfloat[blabla\label{fig:fusion1}]{
\includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
}\\
\hspace{10pt}
\subfloat[blabla\label{fig:fusion2}]{
\includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
}
\end{center}
\caption{blabla}
\label{fig:fusion}
\end{figure}

%\begin{figure}[!h]\begin{center}
%  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
%  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations, with and without fusions proposed by MSF.}
%  \label{fig:fusion}
%\end{center}\end{figure}
%
%\begin{figure}[!h]\begin{center}
%  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
%  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations, with and without fusions proposed by MSF.}
%  \label{fig:fusion}
%\end{center}\end{figure}

>>>>

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{blabla}
  \label{fig:fusion1}
\end{center}\end{figure}

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{blabla}
  \label{fig:fusion2}
\end{center}\end{figure}
